Analysis of epistatic inflation under large single additive effects, with a focus on the replication rate

### 2019-12-26 null_replication/docs/analyse_results.rmd
updated

@@

```{r}
library(tidyverse)
load("../data/rs67903230.rdata")
res$polygenic <- res$i %% 2 == 0
```

@@

```{r}
plot(lambda_disc ~ lambda_repl, res)
```

@@

@@

```{r}
ggplot(res, aes(x=varexp, y=nsig_disc_bonf)) +
geom_point()
```

@@

@@

```{r}
res$lambda_disc_bin <- Hmisc::cut2(res$lambda_disc, g=30)
group_by(res, lambda_disc_bin) %>% summarise(n=mean(nsig_disc_bonf, na.rm=T)) %>% 
ggplot(aes(x=lambda_disc_bin, y=n)) +
geom_point() +
theme(axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5)) +
labs(x="Simulation's lambda", y="Mean number of discovery hits")
```

@@

repl_rate <- bind_rows(
	group_by(res, lambda_disc_bin) %>% summarise(m=mean(bonf_bonf_rr, na.rm=T)) %>% mutate(threshold="Bonferroni"),
	group_by(res, lambda_disc_bin) %>% summarise(m=mean(bonf_fdr_rr, na.rm=T)) %>% mutate(threshold="FDR"),
	group_by(res, lambda_disc_bin) %>% summarise(m=mean(bonf_bonf2_rr, na.rm=T)) %>% mutate(threshold="Experiment")
)
repl_rate %>% ggplot(aes(x=lambda_disc_bin, y=m, group=threshold)) +
geom_line(aes(colour=threshold)) +
scale_colour_brewer(type="qual") +
theme(axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5)) +
labs(x="Simulation's lambda", y="Replication rate")
```

>>>>

```{r}
suppressWarnings(suppressPackageStartupMessages({
	library(knitr)
	library(tidyverse)
}))
opts_chunk$set(cache=TRUE)
```

@@

```{r}
load("../data/rs67903230.rdata")
res$polygenic <- res$i %% 2 == 0
```

@@

```{r}
ggplot(res, aes(y=lambda_repl, x=lambda_disc)) +
geom_point() +
labs(x = "Genomic inflation (discovery)", y = "Genomic inflation (replication)")
```

@@

```{r}
ggplot(res, aes(x=varexp, y=lambda_disc)) +
geom_point() +
labs(x="Additive variance explained", y="Genomic inflation")
```

@@

```{r}
res$varexp_bin <- Hmisc::cut2(res$varexp, g=30)
ggplot(res, aes(x=varexp_bin, y=nsig_disc_bonf)) +
geom_boxplot() +
theme(axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5)) +
labs(x="Additive variance explained", y="Mean number of discovery hits")
```

@@

```{r}
ggplot(res, aes(x=fstat_cor)) +
geom_histogram(fill="white", colour="black") +
labs(x="Correlation of F statistics between discovery and replication")

```

@@

```{r}
res$lambda_disc_bin <- Hmisc::cut2(res$lambda_disc, g=30)
res %>% 
ggplot(aes(x=lambda_disc_bin, y=nsig_disc_bonf)) +
geom_boxplot() +
theme(axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5)) +
labs(x="Genomic inflation of simulation", y="Mean number of discovery hits")
```

@@

repl_rate <- bind_rows(
	group_by(res, lambda_disc_bin) %>% summarise(m=mean(bonf_bonf_rr, na.rm=T)) %>% mutate(threshold="Bonferroni"),
	group_by(res, lambda_disc_bin) %>% summarise(m=mean(bonf_fdr_rr, na.rm=T)) %>% mutate(threshold="FDR"),
	group_by(res, lambda_disc_bin) %>% summarise(m=mean(bonf_bonf2_rr, na.rm=T)) %>% mutate(threshold="Experiment")
)
repl_rate %>% ggplot(aes(x=lambda_disc_bin, y=m, group=threshold)) +
geom_line(aes(colour=threshold)) +
scale_colour_brewer(type="qual") +
theme(axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5)) +
labs(x="Genomic inflation factor", y="Replication rate")
```
